Blessing of FedAvg's Linear Speedup in Federated Learning

### 2020-05-26 source/main.tex
add linear regression
abs
change to FedAvg

\title{Unified Convergence Analysis of FedAve on Non-IID Data}

@@

% \tableofcontents
\begin{abstract}
Federated learning is a distributed learning paradigm that enables learning a
model jointly over a large number of workers without sharing the private data
on local workers. The characteristics of non-identically distributed data
across the network and low device participation bring significant challenges
in analyzing the convergence of federated learning algorithms. Prior works
have either analyzed the convergence with i.i.d. data, or with full device
participation, and often with suboptimal rates. In this work, we provide a
comprehensive analysis of the convergence rate of Federated Averaging (FedAvg)
with SGD and Nesterov SGD updates for general convex problems with arbitrarily
heterogeneous data. Firstly we show that the convergence rates enjoy a linear
speedup in the number of participating workers for all convex smooth problems
for both algorithms. Furthermore, we propose a new accelerated federated
learning algorithm improving the convergence rate over FedAvg with SGD in the
overparameterized setting. Empirical evaluation of the algorithms in various
settings match our theoretical results.
\end{abstract}

@@

% accelerated 
% convex strongly 
% smooth non-smooth. 
\input{sec_problem}
\input{sec_theorems}
\newpage
\input{sec_exp}
% \input{sec_exp_note}

\newpage
\appendix
\input{sec_overview}
% \input{sec_acceleratedFL}

>>>>

\title{Blessing of FedAvg's Linear Speedup in Federated Learning}

@@

% \tableofcontents
\begin{abstract}
Federated learning is a distributed learning paradigm that enables learning a
model jointly over a large number of workers without sharing the private data
on local workers. The characteristics of non-identically distributed data
across the network and low device participation brings significant challenges
in analyzing the convergence of federated learning algorithms. Prior works
have either analyzed the convergence with i.i.d. data, or with full device
participation, and often with suboptimal rates. In this work, we provide a
comprehensive analysis of the convergence rate of Federated Averaging (FedAvg)
with SGD and Nesterov SGD updates for general convex problems with arbitrarily
heterogeneous data. Firstly we show that the convergence rates enjoy a linear
speedup in the number of participating workers for all convex smooth problems
for both algorithms. Furthermore, we propose a new accelerated federated
learning algorithm improving the convergence rate over FedAvg with SGD in the
overparameterized setting. Empirical evaluation of the algorithms in various
settings match our theoretical results.
\end{abstract}

@@

% accelerated 
% convex strongly 
% smooth non-smooth. 
\input{sec_intro}
\input{sec_problem}
\input{sec_strongly_convex_smooth}
\input{sec_convex_smooth}
\input{sec_linear_regression}
\input{sec_exp}

\newpage
\appendix
\input{sec_appendix}
% \input{sec_acceleratedFL}

### 2020-05-26 source/sec_cvxnonsm.tex
change cvx smooth assumption to variance
change to FedAvg

\begin{theorem}
	Let Assumption~\ref{ass:subgrad2} hold, 
	then the FedAve with partial device participation satisfies
	\begin{align}
		 \EE[F^*_t] - F^* &\leq  \left(\frac{\Delta_0[C+ G^2 \left(3 + 4(E-1)^2\right)]}{T}\right)^{1/2}
	\end{align}
	where $\eta_t = \eta_t  = \sqrt{ \frac{\Delta_0}{T[C+ G^2 \left(3 + 4(E-1)^2\right)]}}$,
	$F^*_t \coloneqq \min_{t \in [0, T-1]} F(\overline{\vw}_t)$.
	% $R = \sqrt{ \frac{\Delta_0}{L}},$
	% $L=\sum_{k=1}^N \left( G^2 \left(3 + 4(E-1)^2\right)\right).$
	% \label{th:cvxnonsmoth}
\end{theorem}
\begin{proof}
% In full device active setting, we have $\overline{\vw}_{t+1}=\overline{\vv}_{t+1}$,
Follow the same reasoning in the proof of Theorem~\ref{th:sgdcvxsmth} \eq{\ref{eq:expandsgd}}, we have
\begin{align}
\EE\left[\left\|\bar{\vv}_{t+1}-\vw^{*}\right\|^2| \vw_{t}\right]=\|\bar{\vw}_{t}-\vw^{*}\|^{2}-2 \eta_{t} \EE \vg_{t}^{\top}\left(\bar{\vw}_{t}-\vw^{*}\right)+\eta_{t}^{2} \EE\| \vg_{t} \|^{2}	
\label{eq:expand}
\end{align}
Note that since $\EE \vg_t = \EE \sum_{k=1}^{N} p_{k} \vg_{t, k}\left(\vw_{t}^{k}\right) \neq \EE \sum_{k=1}^Np_k \vg_{t,k}(\overline{\vw}_t)$, therefore $\EE \vg_t \notin \partial F(\overline{\vw}_t)$, we cannot directly use the convex definition to
upper bound $- \EE \vg_{t}^{\top}\left(\bar{\vw}_{t}-\vw^{*}\right)$ in \eq{\ref{eq:expand}}, as classic SGD proof did.

@@

Now we plug in \eq{\ref{eq:exp4}} into \eq{\ref{eq:expand}}:
\begin{align}
	\Delta_{t+1} \leq& \|\bar{\vw}_{t}-\vw^{*}\|^{2} + \eta_{t}^{2} \EE\| \vg_{t} \|^{2}  + \eta_t^2 C \\
	& + \underbrace{\sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2}_{A_1} +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2
  - 2\eta_t\underbrace{\sum_{k=1}^N p_k (F_k(\vw_t^k) - F^*)}_{A_2} \label{eq:main2}
\end{align}

@@

Now we bound $A_2$:
\begin{align}
	& \sum_{k=1}^N p_k (F_k(\vw_t^k) - F^*) \\
 = & \sum_{k=1}^N p_k (F_k(\vw_t^k) - F_k(\overline{w}_t) + F_k(\overline{w}_t) - F^*) \\
 = & \sum_{k=1}^N p_k (F_k(\vw_t^k) - F_k(\overline{w}_t) ) + (F(\overline{w}_t) - F^*)\\ 
 \geq & \sum_{k=1}^{N} P_{k}\left<\EE g_{t k}\left(\overline{\vw}_{t}\right), \vw_{t}^k-\overline{\vw}_{t}\right> + (F(\overline{w}_t) - F^*)\\
 \geq& -\frac{1}{2} \sum_{k=1}^{N} P_{k} (\eta_t \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \frac{1}{\eta_t} \|\vw_t^k - \overline{\vw}_t\|^2) + (F(\overline{w}_t) - F^*) \label{eq:a24}
\end{align}
where in fourth line we use Cauchy-Schwarz inequality and AM-GM inequality.

Now we plug in \eq{\ref{eq:a24}} into \eq{\ref{eq:main2}}:
\begin{align}
	\Delta_{t+1} & \leq \Delta_t + 
	\eta_{t}^{2} \EE\| \vg_{t} \|^{2} + \sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2 +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2 + \eta_t^2 C \\
	 &- 2 \eta_t \left(-\frac{1}{2} \sum_{k=1}^{N} P_{k} (\eta_t \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \frac{1}{\eta_t} \|\vw_t^k - \overline{\vw}_t\|^2) + (F(\overline{w}_t) - F^*) \right)  + \eta_t^2 C \\
	& \leq \Delta_t + 
	\eta_{t}^{2} \EE\| \vg_{t} \|^{2} + \sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2 +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2  + \eta_t^2 C  \\
	& +\sum_{k=1}^{N} P_{k} (\eta_t^2 \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \|\vw_t^k - \overline{\vw}_t\|^2) - 2\eta_t (F(\overline{w}_t) - F^*) \\
	& = \Delta_t + \underbrace{\eta_{t}^{2} \EE\| \vg_{t} \|^{2} +\sum_{k=1}^N p_k  ( 2\|\overline{\vw}_t - \vw_t^k\|^2  +  \eta_t^2 \|\EE \vg_{t,k}\|^2 + \eta_t^2 \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 ) + \eta_t^2 C }_{\eta_t^2C_1}  - 2\eta_t (F(\overline{w}_t) - F^*) \label{eq:main3}
\end{align}
Apply Lemma~\ref{lma:gradient} and Lemma~\ref{lma:l3iclr} in the last line, we can bound $C_1$ as follows:
\begin{align}
\eta_t^2 C_1  = \eta_t^2 [\sum_{k=1}^N p_k G_k^2 \left(3 + 4(E-1)^2\right) + C]  = \eta_t^2 [C+ G^2 \left(3 + 4(E-1)^2\right)]
\end{align}
Rearrange the last inequality:
\begin{align}
	2\eta_t (\EE[F(\overline{w}_t)] - F^*) \leq \Delta_t - \Delta_{t+1} + \eta_t^2 C_1 
\end{align}
Sum over two sides from $t=0$ to $t = T- 1$ and define $F^*_t \coloneqq \min_{t \in [0, T-1]} F(\overline{\vw}_t)$
\begin{align}
	\sum_{t=0}^{T-1} 2\eta_t(\EE[F(\overline{w}_t)] - F^*) & \leq \Delta_0 - \Delta_T + \sum_{t=0}^{T-1} \eta_t^2 C_1 \\
	\sum_{t=0}^{T-1} 2\eta_t(\EE[F(\overline{w}_t)]- F^*) & \leq \Delta_0 + \sum_{t=0}^{T-1} \eta_t^2 C_1 \\
    \EE[F^*_t] - F^* &\leq \frac{\Delta_0 + \sum_{t=0}^{T-1} \eta_t^2C_1 }{ \sum_{t=0}^{T-1}  2 \eta_t}\\
    \EE[F^*_t] - F^* &\leq  \left(\frac{\Delta_0[C+ G^2 \left(3 + 4(E-1)^2\right)]}{T}\right)^{1/2}
\end{align}
where in last line we let $\eta_t  = \sqrt{ \frac{\Delta_0}{T[C+ G^2 \left(3 + 4(E-1)^2\right)]}}$.

>>>>

\begin{theorem}
	Let Assumption~\ref{ass:subgrad2} hold, 
	then the FedAvg with partial device participation satisfies
	\begin{align}
		 \EE[F^*_t] - F^* &\leq  \left(\frac{\Delta_0[C+ G^2 \left(3 + 4(E-1)^2\right)]}{T}\right)^{1/2}
	\end{align}
	where $\eta_t = \eta_t  = \sqrt{ \frac{\Delta_0}{T[C+ G^2 \left(3 + 4(E-1)^2\right)]}}$,
	$F^*_t \coloneqq \min_{t \in [0, T-1]} F(\overline{\vw}_t)$.
	% $R = \sqrt{ \frac{\Delta_0}{L}},$
	% $L=\sum_{k=1}^N \left( G^2 \left(3 + 4(E-1)^2\right)\right).$
	% \label{th:cvxnonsmoth}
\end{theorem}
\begin{proof}
% In full device active setting, we have $\overline{\vw}_{t+1}=\overline{\vv}_{t+1}$,
Follow the same reasoning in the proof of Theorem~\ref{th:sgdcvxsmth} \eq{\ref{eq:expandsgd}}, we have
\begin{align}
\EE\left[\left\|\bar{\vv}_{t+1}-\vw^{*}\right\|^2| \vw_{t}\right]=\|\bar{\vw}_{t}-\vw^{*}\|^{2}-2 \eta_{t} \EE \vg_{t}^{\top}\left(\bar{\vw}_{t}-\vw^{*}\right)+\eta_{t}^{2} \EE\| \vg_{t} \|^{2}	
\label{eq:expand}
\end{align}
Note that since $\EE \vg_t = \EE \sum_{k=1}^{N} p_{k} \vg_{t, k}\left(\vw_{t}^{k}\right) \neq \EE \sum_{k=1}^Np_k \vg_{t,k}(\overline{\vw}_t)$, therefore $\EE \vg_t \notin \partial F(\overline{\vw}_t)$, we cannot directly use the convex definition to
upper bound $- \EE \vg_{t}^{\top}\left(\bar{\vw}_{t}-\vw^{*}\right)$ in \eq{\ref{eq:expand}}, as classic SGD proof did.

@@

Now we plug in \eq{\ref{eq:exp4}} into \eq{\ref{eq:expand}}:
\begin{align}
	\Delta_{t+1} \leq& \|\bar{\vw}_{t}-\vw^{*}\|^{2} + \eta_{t}^{2} \EE\| \vg_{t} \|^{2}  + \eta_t^2 C \\
	& + \underbrace{\sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2}_{A_1} +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2
  - 2\eta_t\underbrace{\sum_{k=1}^N p_k (F_k(\vw_t^k) - F^*)}_{A_2} \label{eq:cvxmain2}
\end{align}

@@

Now we bound $A_2$:
\begin{align}
	& \sum_{k=1}^N p_k (F_k(\vw_t^k) - F^*) \\
 = & \sum_{k=1}^N p_k (F_k(\vw_t^k) - F_k(\overline{w}_t) + F_k(\overline{w}_t) - F^*) \\
 = & \sum_{k=1}^N p_k (F_k(\vw_t^k) - F_k(\overline{w}_t) ) + (F(\overline{w}_t) - F^*)\\ 
 \geq & \sum_{k=1}^{N} P_{k}\left<\EE g_{t k}\left(\overline{\vw}_{t}\right), \vw_{t}^k-\overline{\vw}_{t}\right> + (F(\overline{w}_t) - F^*)\\
 \geq& -\frac{1}{2} \sum_{k=1}^{N} P_{k} (\eta_t \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \frac{1}{\eta_t} \|\vw_t^k - \overline{\vw}_t\|^2) + (F(\overline{w}_t) - F^*) \label{eq:cvxa24}
\end{align}
where in fourth line we use Cauchy-Schwarz inequality and AM-GM inequality.

Now we plug in \eq{\ref{eq:cvxa24}} into \eq{\ref{eq:cvxmain2}}:
\begin{align}
	\Delta_{t+1} & \leq \Delta_t + 
	\eta_{t}^{2} \EE\| \vg_{t} \|^{2} + \sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2 +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2 + \eta_t^2 C \\
	 &- 2 \eta_t \left(-\frac{1}{2} \sum_{k=1}^{N} P_{k} (\eta_t \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \frac{1}{\eta_t} \|\vw_t^k - \overline{\vw}_t\|^2) + (F(\overline{w}_t) - F^*) \right)  + \eta_t^2 C \\
	& \leq \Delta_t + 
	\eta_{t}^{2} \EE\| \vg_{t} \|^{2} + \sum_{k=1}^N p_k \|\overline{\vw}_t - \vw_t^k\|^2 +  \sum_{k=1}^N p_k \eta_t^2 \|\EE \vg_{t,k}\|^2  + \eta_t^2 C  \\
	& +\sum_{k=1}^{N} P_{k} (\eta_t^2 \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 + \|\vw_t^k - \overline{\vw}_t\|^2) - 2\eta_t (F(\overline{w}_t) - F^*) \\
	& = \Delta_t + \underbrace{\eta_{t}^{2} \EE\| \vg_{t} \|^{2} +\sum_{k=1}^N p_k  ( 2\|\overline{\vw}_t - \vw_t^k\|^2  +  \eta_t^2 \|\EE \vg_{t,k}\|^2 + \eta_t^2 \|\EE \vg_{t,k}(\overline{\vw}_t) \|^2 ) + \eta_t^2 C }_{\eta_t^2C_1}  - 2\eta_t (F(\overline{w}_t) - F^*) \label{eq:main3}
\end{align}
Apply Lemma~\ref{lma:gradient} and Lemma~\ref{lma:l3iclr} in the last line, we can bound $C_1$ as follows:
\begin{align}
\eta_t^2 C_1  = \eta_t^2 [\sum_{k=1}^N p_k G_k^2 \left(3 + 4(E-1)^2\right) + C]  = \eta_t^2 [C+ G^2 \left(3 + 4(E-1)^2\right)]
\end{align}
Rearrange the last inequality:
\begin{align}
	2\eta_t (\EE[F(\overline{w}_t)] - F^*) \leq \Delta_t - \Delta_{t+1} + \eta_t^2 C_1 
\end{align}
Sum over two sides from $t=0$ to $t = T- 1$ and define $F^*_t \coloneqq \min_{t \in [0, T-1]} F(\overline{\vw}_t)$
\begin{align}
	\sum_{t=0}^{T-1} 2\eta_t(\EE[F(\overline{w}_t)] - F^*) & \leq \Delta_0 - \Delta_T + \sum_{t=0}^{T-1} \eta_t^2 C_1 \\
	\sum_{t=0}^{T-1} 2\eta_t(\EE[F(\overline{w}_t)]- F^*) & \leq \Delta_0 + \sum_{t=0}^{T-1} \eta_t^2 C_1 \\
    \EE[F^*_t] - F^* &\leq \frac{\Delta_0 + \sum_{t=0}^{T-1} \eta_t^2C_1 }{ \sum_{t=0}^{T-1}  2 \eta_t}\\
    \EE[F^*_t] - F^* &\leq  \left(\frac{\Delta_0[C+ G^2 \left(3 + 4(E-1)^2\right)]}{T}\right)^{1/2}
\end{align}
where in last line we let $\eta_t  = \sqrt{ \frac{\Delta_0}{T[C+ G^2 \left(3 + 4(E-1)^2\right)]}}$.

### 2020-05-26 source/sec_exp.tex
change to FedAvg

In this section, we empirically examine the theoretical convergence rate of FedAve on various scenarios, including strongly convex function, convex smooth function, and overparameterized setting, as presented in previous sections.

@@

\begin{figure}
\centering
	\begin{tabular}{ccc}
	\hspace{-2em}\includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupNodesT-min-w8a-epsilon0131-reg1e-05.pdf} &
\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupNodesT-min-w8a-epsilon0134-reg0.pdf} &
\includegraphics[width=0.33\textwidth]{fig/paper-linregressionspeedupNodesT-min-linearregressionw8a-epsilon002-reg0.pdf}\\
(a) Strongly convex objective & (b) Convex smooth objective & (c) Linear regression
	\end{tabular}
\caption{The linear speedup convergence of FedAve w.r.t the number of nodes. }
\label{fig:speedup}
\end{figure}

\begin{figure}
\centering
	\begin{tabular}{ccc}
	\hspace{-2em} \includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsT-min-w8a-epsilon0131-reg1e-05.pdf} &
	\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupEpochsT-min-w8a-epsilon0134-reg0.pdf} & 
	\includegraphics[width=0.33\textwidth]{fig/paper-linregressionspeedupEpochsT-min-linearregressionw8a-epsilon002-reg0.pdf} \\
	\hspace{-2em} \includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsRounds-min-w8a-epsilon0131-reg1e-05.pdf} &
	\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupEpochsRounds-min-w8a-epsilon0134-reg0.pdf} & 
	\includegraphics[width=0.33\textwidth]{fig/paper-linregression-newspeedupEpochsRounds-min-linearregressionw8a-epsilon002-reg0.pdf} \\
(a) Strongly convex objective & (b) Convex smooth objective & (c) Linear regression
	\end{tabular}
\caption{The convergence of FedAve w.r.t the number of epochs. }
\label{fig:e}
\end{figure}

>>>>

In this section, we empirically examine the theoretical convergence rate of FedAvg on various scenarios, including strongly convex function, convex smooth function, and overparameterized setting, as presented in previous sections.

@@

\begin{figure}
\centering
	\begin{tabular}{ccc}
	\hspace{-2em}\includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupNodesT-min-w8a-epsilon0131-reg1e-05.pdf} &
\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupNodesT-min-w8a-epsilon0134-reg0.pdf} &
\includegraphics[width=0.33\textwidth]{fig/paper-linregressionspeedupNodesT-min-linearregressionw8a-epsilon002-reg0.pdf}\\
(a) Strongly convex objective & (b) Convex smooth objective & (c) Linear regression
	\end{tabular}
\caption{The linear speedup convergence of FedAvg w.r.t the number of nodes. }
\label{fig:speedup}
\end{figure}

\begin{figure}
\centering
	\begin{tabular}{ccc}
	\hspace{-2em} \includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsT-min-w8a-epsilon0131-reg1e-05.pdf} &
	\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupEpochsT-min-w8a-epsilon0134-reg0.pdf} & 
	\includegraphics[width=0.33\textwidth]{fig/paper-linregressionspeedupEpochsT-min-linearregressionw8a-epsilon002-reg0.pdf} \\
	\hspace{-2em} \includegraphics[width=0.33\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsRounds-min-w8a-epsilon0131-reg1e-05.pdf} &
	\includegraphics[width=0.33\textwidth]{fig/paper-cvxsmoothspeedupEpochsRounds-min-w8a-epsilon0134-reg0.pdf} & 
	\includegraphics[width=0.33\textwidth]{fig/paper-linregression-newspeedupEpochsRounds-min-linearregressionw8a-epsilon002-reg0.pdf} \\
(a) Strongly convex objective & (b) Convex smooth objective & (c) Linear regression
	\end{tabular}
\caption{The convergence of FedAvg w.r.t the number of epochs. }
\label{fig:e}
\end{figure}

### 2020-05-26 source/sec_theorems.tex
MaSS_linear_speedup
change to FedAvg

@@

\section{The Convergence of FedAve for General Convex Functions}
This section summarizes the convergence of FedAve.
The updates of FedAve with partial device activation is given by: 
\begin{align} 
\mathbf{v}_{t+1}^{k} &=\mathbf{w}_{t}^{k}-\eta_{t} \nabla F_{k}\left(\mathbf{w}_{t}^{k}, \xi_{t}^{k}\right) \\ \mathbf{w}_{t+1}^{k} &=\left\{\begin{array}{ll}\mathbf{v}_{t+1}^{k} & \text { if } t+1 \notin \mathcal{I}_{E}, \\ 
\sum_{k \in \cS_{t+1}} \mathbf{v}_{t+1}^{k} & \text { if } t+1 \in \mathcal{I}_{E}\end{array}\right.
\end{align}

\subsection{The Convergence of FedAve for Convex Functions}
In this subsection, we discuss the convergence of FedAve for convex functions,
we consider both smooth (Theorem~\ref{th:sgdcvxsmth}) and non-smooth (Theorem~\ref{th:sgdcvxnonsmoth})
functions.

@@

\subsection{The Convergence of FedAve for Strongly Convex Functions}

>>>>

Linear speedup of SGD and MaSS for linear regression, full participation: 
\begin{align*}
\|\overline{w}_{t+1}-w^{\ast}\|^{2} & \leq C\cdot\exp(-\frac{t}{\sqrt{(\kappa_{N}+(E-1)^{2})(\tilde{\kappa}_{N}+(E-1)^{2})}})
\end{align*}

 which implies that for $E=1$, there is linear speedup, i.e. 
\begin{align*}
\|\overline{w}_{t+1}-w^{\ast}\|^{2} & \leq C\cdot\exp(-\frac{t}{\sqrt{(\kappa_{N})(\tilde{\kappa}_{N})}})\leq C\cdot\exp(-\frac{Nt}{\sqrt{(\kappa_{1})(\tilde{\kappa})}})
\end{align*}
when $N$ satifies $N=O(\min(L_{1}/L,\tilde{\kappa}))$, and for $(E-1)^{2}\leq\min(\kappa_{N},\tilde{\kappa}_{N})$,
\begin{align*}
\|\overline{w}_{t+1}-w^{\ast}\|^{2} & \leq C\cdot\exp(-\frac{Nt}{4\sqrt{\kappa_{1}\tilde{\kappa}}})
\end{align*}

@@

\section{The Convergence of FedAvg for General Convex Functions}
This section summarizes the convergence of FedAvg.
The updates of FedAvg with partial device activation is given by: 
\begin{align} 
\mathbf{v}_{t+1}^{k} &=\mathbf{w}_{t}^{k}-\eta_{t} \nabla F_{k}\left(\mathbf{w}_{t}^{k}, \xi_{t}^{k}\right) \\ \mathbf{w}_{t+1}^{k} &=\left\{\begin{array}{ll}\mathbf{v}_{t+1}^{k} & \text { if } t+1 \notin \mathcal{I}_{E}, \\ 
\sum_{k \in \cS_{t+1}} \mathbf{v}_{t+1}^{k} & \text { if } t+1 \in \mathcal{I}_{E}\end{array}\right.
\end{align}

\subsection{The Convergence of FedAvg for Convex Functions}
In this subsection, we discuss the convergence of FedAvg for convex functions,
we consider both smooth (Theorem~\ref{th:sgdcvxsmth}) and non-smooth (Theorem~\ref{th:sgdcvxnonsmoth})
functions.

@@

\subsection{The Convergence of FedAvg for Strongly Convex Functions}
